---
title: 'Monte Carlo Simulation: Jin and Vasserman (2021)'
author: "Yuki KAYABA"
date: "2/26/2023"
site: bookdown::bookdown_site
output:
  bookdown::gitbook: default
#output_dir: docs
#bookdown::gitbook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bookdown)
library(magrittr)
library(MASS)
```

# Generate Data

The model is divided into two parts: choice model and cost model. First we generate data related to cost model and then we generate data related to choice model.

1. Generate $\lambda_{imt}$. $\lambda_{imt}$ is one of the most significant variables that represents consumer's risk (observable for consumers but not econometrician)
2. Generate choice in $t = 0$ according to the choice model. In $t = 0$, consumers have four options: the firm with and without monitoring, competitor 1 and 2.
3. Generate cost realization (claims count, severity and monitoring score) in $t = 0$ according to the cost model. 

## Generate $\lambda$

- The rate parameter, $\lambda_{imt}$ of Poisson distributed claims count, has mean $\mu_{\lambda, imt}$ and an additive error $\varepsilon_{\lambda, i}$ which is log-normally distributied with spread $\sigma_{\lambda}$
- We assume that $\mu_{\lambda, imt} = \theta_{\lambda1}x_{1, imt} + \cdots + \theta_{\lambda4}x_{4, imt}$ 

```{r generate lambda}
N <- 1000
T <- 1
D <- 3
J <- 4 ## The number of products. 

## True Parameters
sigma_lambda <- 0.1
theta_lambda <- c(1, 0.5, 1, 2)

## Covariates
mu_x_t0_m0 <- rep(-1, 4)
mu_x_t0_m1 <- rep(-2, 4)
mu_x_t1_m0 <- rep(0, 4)
mu_x_t1_m1 <- rep(0, 4)
sigma_x <- diag(0.5, 4)

X_t0_m0 <- mvrnorm(N, mu_x_t0_m0, sigma_x)
X_t0_m1 <- X_t0_m0 + 0.1*mvrnorm(N, mu_x_t0_m1, sigma_x)
X_t1_m0 <- X_t0_m0 + 0.5*mvrnorm(N, mu_x_t1_m0, sigma_x)
X_t1_m1 <- 0.5*X_t0_m0 + 0.5*X_t0_m1 + 0.5*mvrnorm(N, mu_x_t1_m1, sigma_x)

X <- X_t0_m0 %>% 
  rbind(X_t0_m1) %>% 
  rbind(X_t1_m0) %>% 
  rbind(X_t1_m1)

colnames(X) <- c(paste("x", 1:4, sep = "_"))

X_lambda <- expand.grid(i = 1:N, m = 0:1, t = 0:1) %>% 
  tibble::as_tibble() %>% 
  cbind(X)

## mu_lambda
mu_lambda <- X_lambda %>% 
  dplyr::mutate(mu_lambda = theta_lambda[1]*x_1 + theta_lambda[2]*x_2 + theta_lambda[3]*x_3 + theta_lambda[4]*x_4)

## epsilon_lambda
epsilon_lambda <- expand.grid(i = 1:N) %>% 
  tibble::as_tibble() %>% 
  dplyr::mutate(epsilon_lambda = rnorm(N, 0, sigma_lambda))

## lambda
lambda <- mu_lambda %>% 
  dplyr::left_join(epsilon_lambda, key = c("i")) %>% 
  dplyr::mutate(lambda = exp(mu_lambda + epsilon_lambda))

```

## Generate Choice in $t = 0$

In the paper, consumer's realized choice utility is modeled as follows: 

$$
\begin{align}
u_{idt}(C, s) &= u_{\gamma}(w_{it} + h_{idt}(C, s)) \\
h_{idt}(C, s) &= -p_{idt} - \mathbf{1}_{d, t-1} \cdot \psi_{idt} - e(C, y_{d}) - p_{idt} \cdot R_{idt}(C, s) \\
\text{where} \quad \psi_{idt} &= \mathbf{1}_{d, t-1} \cdot \eta_{0} + \mathbf{1}_{f_{d}, t-1} \cdot \eta_{it} + \mathbf{1}_{m_{d}} \cdot \mathbf{1}_{t=0} \cdot \xi_{it}
\end{align}
$$

- Each Claim has a stochastic cost $l$, drawn from an independent Pareto distribution
- The monitoring score $s$ is drawn according to a log-normal distribution with mean $\mu_{s, i}$ and precision $\sigma_{s}$

# Estimation

