---
title: 'Monte Carlo Simulation: Jin and Vasserman (2021)'
author: "Yuki KAYABA"
date: "2/26/2023"
site: bookdown::bookdown_site
output:
  bookdown::gitbook: default
#output_dir: docs
#bookdown::gitbook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, cache = FALSE)
library(bookdown)
library(magrittr)
library(MASS)
```

# Generate Data

First we generate data in the following procedure.

1. Generate $\lambda_{imt}$. $\lambda_{imt}$ is one of the most significant variables that represents consumer's risk (observable for consumers but not econometrician)
2. Generate choice in $t = 0$ according to the choice model. In $t = 0$, consumers have four options: the firm with and without monitoring, competitor 1 and 2.
3. Generate realization of cost (claims count, severity and monitoring score) in $t = 0$ according to the cost model. 

## Generate $\lambda$

- The rate parameter, $\lambda_{imt}$ of Poisson distributed claims count, has mean $\mu_{\lambda, imt}$ and an additive error $\varepsilon_{\lambda, i}$ which is log-normally distributied with spread $\sigma_{\lambda}$
- We assume that $\mu_{\lambda, imt} = \theta_{\lambda1}x_{1, imt} + \cdots + \theta_{\lambda4}x_{4, imt}$ 

```{r generate lambda}
rm(list = ls())

N <- 1000
T <- 1
D <- 4

# set the seed
set.seed(1)

## True Parameters
sigma_lambda <- 0.1
theta_lambda <- c(1, 0.5, 1, 2, -0.5)

## Covariates
mu_x_t0 <- rep(-1, 4)
mu_x_t1 <- rep(0, 4)
sigma_x <- diag(0.5, 4)

X_t0 <- mvrnorm(N, mu_x_t0, sigma_x)
X_t1 <- 0.5*X_t0 + 0.5*mvrnorm(N, mu_x_t1, sigma_x)

X <- X_t0 %>% 
  rbind(X_t0) %>% 
  rbind(X_t1) %>% 
  rbind(X_t1)

colnames(X) <- c(paste("x", 1:4, sep = "_"))

X_lambda <- expand.grid(i = 1:N, m = 0:1, t = 0:1) %>% 
  tibble::as_tibble() %>% 
  cbind(X)

## mu_lambda
mu_lambda <- X_lambda %>% 
  dplyr::mutate(mu_lambda = theta_lambda[1]*x_1 + theta_lambda[2]*x_2
                + theta_lambda[3]*x_3 + theta_lambda[4]*x_4
                + theta_lambda[5]*ifelse(m == 0 & t == 0, 1, 0))

## epsilon_lambda
epsilon_lambda <- expand.grid(i = 1:N) %>% 
  tibble::as_tibble() %>% 
  dplyr::mutate(epsilon_lambda = rnorm(N, 0, sigma_lambda))

## lambda
lambda <- mu_lambda %>% 
  dplyr::left_join(epsilon_lambda, key = c("i")) %>% 
  dplyr::mutate(lambda = exp(mu_lambda + epsilon_lambda))

```

## Generate (Expectation of) Monitoring Score and Severity

```{r cost model}

##
theta_score <- c(1, -0.5, 2, 1)
sigma_score <- 1

score <- lambda %>% 
  dplyr::filter(t == 0, m == 1) %>% 
  dplyr::mutate(mu_score = theta_score[1] + theta_score[2]*log(lambda)
                + theta_score[3]*x_1 + theta_score[4]*x_2,
                E_score = exp(mu_score + sigma_score^2 / 2)) %>% 
  dplyr::select(i, m, t, mu_score, E_score)

## Expectation of Out-of-Pocket
policy_limit <- 1000
l0 <- 500
a_l <- 2.5

oop <- lambda %>% 
  dplyr::mutate(prob_C1 = lambda * exp(-lambda),
                E_oop = prob_C1 * (l0^(a_l)/(a_l - 1))*policy_limit^(-a_l + 1)) %>% 
  dplyr::select(i, m, t, E_oop)

summary(oop)
```

## Generate Choice in $t = 0$

- In the paper, consumer's realized choice utility is modeled as follows: 

$$
\begin{align}
u_{idt}(C, s) &= u_{\gamma}(w_{it} + h_{idt}(C, s)) \\
h_{idt}(C, s) &= -p_{idt} - \mathbf{1}_{d, t-1} \cdot \psi_{idt} - e(C, y_{d}) - p_{idt} \cdot R_{idt}(C, s) \\
\text{where } \psi_{idt} &= \mathbf{1}_{d, t-1} \cdot \eta_{0} + \mathbf{1}_{f_{d}, t-1} \cdot \eta_{it} + \mathbf{1}_{m_{d}} \cdot \mathbf{1}_{t=0} \cdot \xi_{it}
\end{align}
$$

- At each period $t$, consumer $i$ chooses $d$ so as to maximize her expected utility:

$$
\begin{align}
d_{it} &= \mathop{\rm argmax}\limits_{d \in D_{it}} \left\{ v_{idt} + \varepsilon_{idt} \right\} \\
\text{where } v_{idt} &= \mathbb{E}_{C, s}[u_{idt}(C, s)] = \mathbb{E}[h_{idt}] -\frac{\gamma}{2}\mathbb{E}[h_{idt}^{2}]
\end{align}
$$

- Thus, we start with generating each component of $h_{idt}$.

```{r generate choice}

price_par_t0_d1 <- c(2, 3, 1, -1)
price_par_t0_d2 <- c(2, 3, 1, -1)
price_par_t0_d3 <- c(1, 2, 3, -1)
price_par_t0_d4 <- c(3, 1, 2, -1)

price_gen_d <- function(choice_t0, D, price_par_t0){
  output <- choice_t0 %>% 
    dplyr::filter(d == D) %>% 
    dplyr::mutate(price = 
                    price_par_t0[1]*x_1 + 
                    price_par_t0[2]*x_2 + 
                    price_par_t0[3]*x_3 +
                    price_par_t0[3]*m +
                    rnorm(1, 10, 1)) %>% 
    dplyr::select(i, d, t, m, f, price)
}

## Generate Price
price_gen_t0 <- function(choice_t0,
                         price_par_t0_d1, price_par_t0_d2,
                         price_par_t0_d3, price_par_t0_d4){
  
  price <- price_gen_d(choice_t0, 1, price_par_t0_d1) %>% 
    rbind(price_gen_d(choice_t0, 2, price_par_t0_d2)) %>% 
    rbind(price_gen_d(choice_t0, 3, price_par_t0_d3)) %>% 
    rbind(price_gen_d(choice_t0, 4, price_par_t0_d4))
  
  output <- choice_t0 %>% 
    dplyr::left_join(price, by = c("i", "d", "t", "m", "f"))
  
  return(output) 
}

## Generate Prior Firm

prior_firm <- expand.grid(i = 1:N) %>% 
  tibble::as_tibble() %>% 
  dplyr::mutate(prior_firm = sample(1:4, size = N, replace = T, prob = c(0, 0.4, 0.35, 0.25)))

## Generate Renewal Price

alpha_m0 <- c(10, 3, 2)
alpha_m1 <- c(10, 3, 3, -0.1)
beta <- 5

## Generate Inertia

eta_f <- c(5, 1, 2, -1)
xi <- c(1, -2)

choice_t0 <- expand.grid(i = 1:N, d = 1:D, t = 0) %>% 
  tibble::as_tibble() %>% 
  dplyr::mutate(m = ifelse(d == 1, 1, 0),
                f = dplyr::case_when(
                  d <= 2 ~ 1,
                  d == 3 ~ 2,
                  d == 4 ~ 3)) %>% 
  dplyr::left_join(lambda, by = c("i", "m", "t")) %>% 
  dplyr::left_join(score, by = c("i", "m", "t")) %>% 
  dplyr::left_join(oop, by = c("i", "m", "t")) %>% 
  price_gen_t0(price_par_t0_d1, price_par_t0_d2, price_par_t0_d3, price_par_t0_d4) %>% 
  dplyr::left_join(prior_firm, by = c("i")) %>% 
  dplyr::mutate(inertia = eta_f[1] + eta_f[2]*x_1 + eta_f[3]*x_2 + eta_f[4]*x_3,
                monitoring_disutility = xi[1] + xi[2]*log(lambda),
                demand_friction = ifelse(d == prior_firm, 0, inertia) + 
                  ifelse(d == 1, monitoring_disutility, 0)) %>% 
  dplyr::mutate(R = ifelse(m == 0, 
                           (alpha_m0[1] + alpha_m0[2]*x_1 + alpha_m0[3]*x_2) / beta,
                           (alpha_m1[1] + alpha_m1[2]*x_1 + alpha_m1[3]*x_2 + alpha_m1[4]*E_score) / beta),
                E_renewal_price = price * R) %>% 
  dplyr::mutate(h = - price - demand_friction - E_oop - E_renewal_price)

# draw idiosyncratic shocks
e <- evd::rgev(dim(choice_t0)[1])

choice_t0 <- cbind(choice_t0, e) %>% 
  dplyr::mutate(u = h + e) %>% 
  dplyr::group_by(i, t) %>% 
  dplyr::mutate(choice = ifelse(u == max(u), 1, 0)) %>% 
  dplyr::ungroup()

summary(choice_t0)

summarize_choice <- choice_t0 %>% 
  dplyr::group_by(d) %>% 
  dplyr::summarise(choice = mean(choice))

summarize_choice
```

## Generate Realization of Cost in $t = 0$

- Each Claim has a stochastic cost $l$, drawn from an independent Pareto distribution
- The monitoring score $s$ is drawn according to a log-normal distribution with mean $\mu_{s, i}$ and precision $\sigma_{s}$

# Estimation

